Introducing ICBe: An Event Extraction Dataset from Narratives about International Crises

### 2023-08-20 replication_paper/psrm_draft/ICBe_manuscript.Rmd
TLS R&R

As we are not the first to attempt to measure international relations in a structured manner, the columns of Table 1 compare the ontological coverage of ICBe to existing state of the art systems in production and with global coverage. We choose these datasets and models as they represent frequently used and reputable efforts to structure and describe historical events of interest to scholars of international politics. The first column starts with our contribution, ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, and the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010]. There is imperfect overlap concerning their intended depth and scope of coverage; 'international crises' are similar, but not identical to, 'interstate wars' and 'militarized interstate disputes' which differ yet again from 'individual events of organized violence' and 'non-violent action'. Even like-concepts require care in comparison, as an 'aim' in ICBe is the same as in MIPS, but an 'alert' in ICBe is not the same as an 'alert' in MID.

@@

```{=tex}
\clearpage
\singlespacing
```
```{r, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}

@@

      #set_table_properties(layout="autofit")  %>%
      vline( i = 1, j = c(3,8), border = NULL, part = "header") %>%
      vline( i = 1:(n), j = 1, border = NULL, part = "body")  %>%
      vline( i = 1:(n), j = c(3,8), border = NULL, part = "body")  %>%

@@

      flextable::width(j = 1, width=0.1)  %>%
      flextable::width( j = 2, width=2) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
      flextable::width( j = 3, width=1.6) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
      flextable::width( j = (4):k, width=0.22) %>%
      flextable::line_spacing( space = 0.5, part = "body") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%
      flextable::rotate(j=1, rotation="tbrl",part="all", align="center") %>%
      #flextable::rotate(j=2, rotation="tbrl",part="all") %>%
      ftExtra::colformat_md(j = 3, part="body")    #Make sure this goes last or it'll get overwritten by the colformat above

@@

# Uncomment for snapshot
# litreview_ft_psrm %>% 
#     #flextable::flextable_to_rmd()
#     save_as_image(path=here::here("replication_paper", "psrm_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
```

>>>>

As we are not the first to attempt to measure international relations in a structured manner, the columns of Table 1 compare the ontological coverage of ICBe to existing state of the art systems in production and with global coverage. We choose these datasets and models as they represent frequently used and reputable efforts to structure and describe historical events of interest to scholars of international politics. The first column starts with our contribution, ICBe, alongside other event-level datasets including CAMEO dictionary lookup-based systems (Historical Phoenix [@althausClineCenterHistorical2019]; ICEWS [@boscheeICEWSCodedEvent2015]; Terrier [@grantOUEventData2017]), the Militarized Interstate Disputes Incidents dataset, the UCDP-GED dataset [@daviesOrganizedViolence19892022; @sundbergIntroducingUCDPGeoreferenced2013], and ACLED [@raleighIntroducingACLEDArmed2010].[^3] The final set of columns compares episode-level datasets beginning with the original ICB project [@brecherInternationalCrisisBehavior2021; @brecherCrisesWorldPolitics1982; @beardsleyInternationalCrisisBehavior2020]; the Militarized Interstate Disputes dataset [@palmerMID5Dataset20112021; @giblerInternationalConflicts181620102018], and the Correlates of War [@sarkeesResortWar181620072010]. We include episode-level datasets as they remain and common and trusted tool for analyzing international relations, and because ICBe is unique among event-level datasets as events are matched to crises and so can be aggregated to the episode level. There is imperfect overlap concerning their intended depth and scope of coverage; 'international crises' are similar, but not identical to, 'interstate wars' and 'militarized interstate disputes' which differ yet again from 'individual events of organized violence' and 'non-violent action'. Even like-concepts require care in comparison, as an 'aim' in ICBe is the same as in MIPS, but an 'alert' in ICBe is not the same as an 'alert' in MID.

@@

```{=tex}
\clearpage
\singlespacing
```
```{r, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=1}

@@

      #set_table_properties(layout="autofit")  %>%
      vline( i = 1, j = c(3,10), border = NULL, part = "header") %>%
      vline( i = 1:(n), j = 1, border = NULL, part = "body")  %>%
      vline( i = 1:(n), j = c(3,10), border = NULL, part = "body")  %>%

@@

      flextable::width(j = 1, width=0.1)  %>%
      flextable::width( j = 2, width=1.8) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
      flextable::width( j = 3, width=1.5) %>% # change width for inline citations for politicalanalysis (4 works, might have extra room)
      flextable::width( j = (4):k, width=0.25) %>%
      flextable::line_spacing( space = 1.0, part = "body") %>% #i=1:nrow(lit_review_alt),
      flextable::padding(padding = 0, part = "body") %>%
      flextable::rotate(j=1, rotation="tbrl",part="all", align="center") %>%
      #flextable::rotate(j=2, rotation="tbrl",part="all") %>%
      ftExtra::colformat_md(j = 3, part="body")    #Make sure this goes last or it'll get overwritten by the colformat above

@@

# Uncomment for snapshot
# litreview_ft_psrm %>% 
     #flextable::flextable_to_rmd()
#     save_as_image(path=here::here("replication_paper", "psrm_draft", "litreview_ft.png"), zoom=1, webshot = "webshot2") # webshot = "webshot2"
```
